### 2020-08-21 README.Rmd
small change
Working on readme edit

run_scbi <- FALSE
run_bw <- TRUE
```

@@

We first load and preprocess the data corresponding to the two census reflecting the time period over which we consider growth in dbh. We load them into R as "tibble" data frames thereby ensuring a standardized input/output format that can be used across all `tidyverse` packages @tidyverse. Furthermore, we ensure that the different variables have the correct names, types (`dbl`, `data`, `factor`).

@@

```{r, eval = run_bw}
# Big Woods
# Read in census data from 2008 & 2014
bw_2008 <- 
  "https://deepblue.lib.umich.edu/data/downloads/z603qx485" %>% 
  read_delim(delim = "\t") %>% 
  mutate(spcode = to_any_case(spcode)) %>%
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )
bw_2014 <- 
  "https://deepblue.lib.umich.edu/data/downloads/1831ck00f" %>% 
  read_delim(delim = "\t") %>% 
  mutate(spcode = to_any_case(spcode)) %>%
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )

@@

```{r, eval = run_bw}
# Big Woods
census_df1 <- bw_2008
# we need to filter out the resprouts
census_df2 <- bw_2014 %>% 
  filter(!str_detect(codes, 'R'))
id <- "treeID"

bw_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>% 
  mutate(sp = to_any_case(sp))
```

@@

@@

```{r, eval = run_bw}
# Bigwoods
# Study region boundary polygon
bw_boundary <- bigwoods_study_region %>% 
  sf_polygon()

# Plot
ggplot() +  
  geom_sf(data = bw_boundary) +
  geom_sf(data = bw_buffer, col="red") +
  # Only random sample of 1000 trees:
  geom_sf(data = bw_growth_df %>% sample_n(1000), aes(col=buffer), size = 0.5)
```

>>>>

run_scbi <- TRUE
run_bw <- FALSE
```

@@

The data for the Big Woods plor are included in the package. For SCBI, we load and preprocess the data corresponding to the two census reflecting the time period over which we consider growth in dbh. We load them into R as "tibble" data frames thereby ensuring a standardized input/output format that can be used across all `tidyverse` packages @tidyverse. Furthermore, we ensure that the different variables have the correct names, types (`dbl`, `data`, `factor`).

@@

```{r, eval = run_bw}
# Big Woods
# Read in census data from 2008 & 2014
data(bw_census_2008, bw_census_2014 )

@@

```{r, eval = run_bw}
# Big Woods
id <- "treeID"

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(sp = to_any_case(sp)) %>%
  # Convert data frame to sf object
  st_as_sf(coords = c("gx", "gy")) %>%
  # drop stemID
  select(-stemID)

@@

We use the function `add_buffer_variable` to identifiy which trees are inside of a buffer region of size `max_dist`.

@@

```{r, eval = run_bw}
# Bigwoods
data(bw_study_region)

# Add buffer variable to data frame
bw_growth_df <- bw_growth_df %>%
  add_buffer_variable(direction = "in", size = max_dist, region = bw_study_region)

ggplot() +
  geom_sf(data = bw_growth_df, aes(col = buffer))
